Online Supporting Information

### 2020-11-25 documents/referee-replies.Rmd

---
title: "Referee Replies"
author: "Dan Ovando"
date: "11/11/2020"
output:
  pdf_document: default
  html_document: default
---

@@

XX Throughout introduction XX

*- A clearer explanation of the gap in the current literature that you are willing to fill is needed*

We have provided a clearer statement of the gap in the current literature that our paper fills on line XX, and line XX

XX Paragraph in intro starting with "While these studies have clearly demonstrated the ability" XX

@@

The key problem here then is not the temporal or spatial variation that BACI-style methods seek to address, but the likely influence of the treatment on the control sites in the context of MPA studies. We have endeavored to make this clearer in the text, on line XX>

XX Paragraph in intro starting with "While these studies have clearly demonstrated the ability" XX

*- Please cite and explain briefly which methods you are using in this article*

We take this to mean a explanation and citation for difference-in-difference. We have included a summary citation for the method (line XX, start of methods), as well as a brief description, given the length constraints of this paper, explaining the link between BACI and difference in difference.

XX paragraph in intro starting with "To fill this important gap"

@@

*- More description on the simulations is needed: how many replicates? How do MPAs were implemented? Are they randomly assigned? How many simulations for each chosen species in the bio-economic model? …?*

Given word limits we unfortunately had to leave many of the details of the simulation model in the supplementary materials. We have however added expanded descriptions of these key attributes in the main text, in particular the nature of the variables requested here, as well as clarifying the role and nature of the simulation model. Line XX
XX Simulation Model part of the methods section XX

*- Please add clear log-ratio and confidence interval equations.*

We apologize but we are not clear what this comment is in reference to. We do not use log-ratios in our model, except in the sense that we use a Bayesian Gamma GLMER with a log link function to run our difference-in-diffecence (basically BACI) , so the estimated effect sizes are in log scales, roughly corresponding to percentage-level effects.

We have however included an equation to clarify the BACI-like nature of our regression, on line XX

XX methods section starting with 
For readers more familiar with BACI methodXX

@@

See @gelman2014a, @mcelreath2020, @hobbs2015, and zuur2009 (for the GLMER terminology).

*- Please explain at least quickly the method of Bayesian regression (or explain the choice of this methods)*

We chose to employ a Bayesian regression as we feel that Bayesian inference has several advantages for program evaluation. Specifically, it allows us to answer questions such as "what is the probability that the Channel Island MPAs had a greater than 0% effect on biomass densities of targeted finfish". For comparison, we have added a frequentist mixed effects version of our model (Fig.SXX), which produces qualitatively the same results XX.

We have briefly addressed our choice of Bayesian methods on line XX

XX end of methods section on diff-in-diff XX

@@

In regards to the difference-in-difference approach, we selected it as it fits the nature of the policy intervention in question: we have a treatment (targeted species) and a control (non-targeted species) observed before and after impact (MPA implementation). As we have sought to clarify on line XX, DiD is for all intents and purposes the same as BACI, which is a commonly used metric in MPA evaluations. We use the term DiD following the vein of @larsen2018, to more closely tie the program evaluation literature in ecology to the econometrics literature that more directly deals with causal inference in program evaluating. Our main methods difference then is in choosing to use targeted and non-targeted species as our treatment and control group, rather than inside and outside MPAs, since we believe there is strong a strong possibility that the MPAs affect the "control" sites outside their borders in the Channel Islands. In addition, because our goal is to estimate the population level effect of the MPAs, and for all of the species evalauted here the population stretches well beyond the borders of the MPAs, we need a control group that is ...

Given the nature of the study, other econometric techniques such as regression discontinuity or instrumental variables are not viable (we do not expect a discontinuous effect given the population dynamcis in play, and we have no valid instrument for the implementation of MPAs that is exogenous to the outcome). Synthetic controls [@abadie] do present another potential solution to our problem, which we use in SM.XX, and find no clear effect.

We have more clearly explained that the DiD approach is more or less identical to a BACI on line XX, which we hope will make this particular model choice seem more familiar.

XX intro to methods, end of diff-in-diff section XX

Results:
*-       Results are unclear and do not fully described what is presented in the figures. Some parts should be in the introduction or method or discussion sections. For instance: you cannot say that the effect is due to size and enforcement because you don’t have tested for that;*

@@

*Line 58: “concentration by the fishing fleet” Shouldn’t it be “concentration of the fishing fleet”? Could you precise where does it concentrate (I assume this is next to MPA sites)*

We have corrected this and clarified the explanation (meaning that if there were 10 boats fishing inside the MPA and 10 boats outside the MPA, closure of the MPA may result in the 10 boats the used to used the MPA moving to the targeted area, so that there are now 20 boats fishing outside the MPA)

*Line 60: “Response ratios can be a highly imprecise and biased measure” You should explain why and what are precisely the problems you target with this method*

We have sought to clarify the specific problem of SUTVA violations (treated MPA sites affecting nearby control sites) that justify why response ratio studies do not necessarily serve as an index of population level effects, and in our methods clarified that it is not the DiD model itself that resolves this problem (which is akin to a BACI), but rather using non-targeted species as the control group, rather than relying on spatial controls. We have also modified the language in that sentence to be more nuanced.

@@

Thank you for pointing out the lack of sufficient detail on the equations for the simulation model. We have restructured the SI so that the simulation model equations are front  and center (SI Line XX), and clarified our explanations of the equations. We have also expanded our description of the simulation model in the text. We hope this clarifies the structure behind the simulation model.

XX Simulation model part of the methods XX

*2) On a related note I didn't come away with a clear sense of the scenarios used to simulate the potential fish outcomes. For example I have no clear sense how you have simulated spatial patterns of fishing intensity.*

We apologize for the confusion in the simulation scenarios. Given the wide array of scenarios employed, and the word constraints of the paper, we unfortunately could not include a thorough description of every scenario in the main text (line XX). We have however included a clearer summary of the simulation in the methods section, highlighting among other key attributes the ways in which we simulate spatial patterns of fishing intensity, which as Referee #2 has noted is a critical variable to consider.

XX Simulation model part of the methods XX

@@

*Similarly, it was not clear to me how you decide which model scenarios are most plausible when conditioning on observed response ratios. Yet conveying the ways in which observed RR could be derived would be useful. There is some discussion of this but not enough to detail. I believe that a good part of the discussion could be removed to make way for this.*

We have expanded our description of the simulation model in an effort to explain this more clearly, and in particular expanded our matching process to address this comment (line XX.). Our Channel Islands simulations were designed to match the genera of species observed in the Channel Islands, our best sense of the exploitation history of those species, and the potential size of the MPAs for those species. For example, we know that all of the finfish species in this analysis are part of populations that span at least the range of the Channel Islands. Since the Channel Islands MPAs make up roughly 20% of the Islands, we know that the MPAs are likely to be no more than 20% of a species range, which we incorporate into the simulations.

For each of these simulations intended to reflect the broad context of the Channel Islands, we sampled the simulated biomass density response ratios. We then matched these simulated response ratios to the empirical response ratios observed in the Channel Islands. So, for example, if we observe a response ratio of 2 after 4 years of protection in the Channel Islands, we matched that results to all simulated results that also had a response ratio of 2 after 4 yearse of MPA protection.

XX see end of simulation model part of methods XX

@@

# Reply to Reviewer 3

Comments to the Author

*This study fills an important gap in knowledge about the seascape wide effects of MPAs on fish populations. The introduction clearly lays out the challenge: we know a lot about how fish biomass increases inside MPAs, but very little about whether this affects seascape scale biomass overall. It uses a novel combination of simulation and empirical modelling to ask if the Channel Islands MPA system has seascape wide effects on fish populations, and under what conditions that might occur.*

We are glad that the reviewer found our contribution important and novel, thank you!

@@

*The simulation model represents on its own a very complete synthesis of the fish biomass MPA modelling literature, and includes most of the processes and their variants, that have been shown over the past 20 years to affect MPA outcomes.*

We are glad you found the simulation model sufficiently comprehensive

*There are some minor comments/edits/clarifications below, but my main questions are about the ‘difference-in-difference model’, which seems to be a type of GLMM. I haven’t heard the term before, so I think it needs a bit more explanation. You might want to move some of the explanation from the SI which was really clear, over to the main text.*

We have moved some of the methods from the SI as suggested, which we hope clarifies what a difference-in-difference is (essentially the same thing as a BACI). We use the term difference-in-difference to tie our results more clearly to the causal inference literature in econometrics. We have also clarified on line XX the clear link between DiD and BACI.

XX DiD methods section XX

@@

Our reasoning for not including a specific interaction term for site, whether that site is an eventual MPA, and whether the MPA is in place in a given year, is that this would muddy the interpretation of our key variable of interest; namely the difference in mean total biomass density of targeted finfish throughout the Islands. Adding in a term representing the presence of an active MPA at a site would effectively mean that the our main coefficient of interest, the interaction of the targeted dummy variable with the year blocks, would represent the mean effect of the MPAs on mean total biomass density of targeted finfish controlling for any effect that those MPAs had inside the MPAs.

XX clarify this messXX

*If it is included, then the predictions for total density should be post-stratified by total area of MPAs in the seascape?*

This is correct. it was quite buried in the SI, but we do weight the MPA and non-MPA sites according to the total area of MPAs in the seascape (SI line XX), since as the referee points out the sampling regime is not random. Otherwise, if the MPAs caused an increase of 50% inside, and 0% outside, given that the PISCO sampling regime has roughly equal sampling inside and outside MPAs, the model would estimate a net effect of 25%, even though MPAs in fact make up roughly 20% of the area.

We have clarified that we weighted the regressions to account for this non-uniform sampling regime on line XX.  We also include an unweighted version of our results, to demonstrate that our results are not sensitive to this weighting choice (Fig.SXX).

XX diff in diff methods XX

@@

*The supplemental materials are very extensive because they include exploration of multiple different model formulations both models, and also a simulation study testing the difference in difference approach. I think you could cut them down a bit if they wanted, and save some of this for more complete exploration in another paper? I think most readers will never get this far, so it seems a bit of a waste to have all this interesting information in a supplemental. The parts I found most in the SI useful for this particular study were the explanation of the DiD, the simulation study and the documentation of the simulation model.*

Thank you for this point! We reorganized the supplemental materials for ease of reading. *However, we have not removed sections at this time. Each of the analyses included in the SM (beyond that basic explanations of the methods) were a result of a question that we received from prior reviewers or peers. As such, we feel that it is better to include these in there for the odd person that really wants to see the results via synthetic controls. Given that the referees primary concern here was our not wasting useful analyses (which we appreciate!), and that we do not intent do dive further into the empirics of this particular question in the Channel Islands at this time, we have elected to go with the conservative approach of a perhaps excessively thorough SM.

@@

Minor comments

*Introduction reads nicely. One comment: it might be worth stating that modelling studies are generally predicting population level effects, but empirical studies are measuring local effects. So another great example of a modelling-empirical disconnect. You’ve set a high expectation in the reader’s mind that you are going to fill this gap, which is then met through the novel combination of simulation and statistical modelling.*

Thank you for this excellent suggestion that we have sought to reflect on line XX.

 XX Introduction XX

@@

*The references are pretty focused on California, and there is certainly a lot of great MPA literature from that part of the world, but perhaps you could expand the geography a bit to make the relevance to international readers clear?* See suggestions below.

Thank you for pointing this out. We only see one suggested reference (Krueck et al. 2017), which we have incorporated on line XX. We have also cited @fulton2015 in order to link our mork more explicitly to the broader literature on MPA simulation model.

@@

*81: thanks for sharing the code. Note doing that does invalidate your double blind.*

We are glad you found it helpful. We did consider this, and decided that the extra effort needed to blind the code itself was not worthwhile. An interesting challenge for journals seeking to do double blind reviews to consider, it's hard to post code that is both open and reproducible and anonymous!

*89: Nils Kruek did a similar thing in his paper, it might be worth reading and relevant citing:https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.2000537*

Thank you for pointing this out, we have included this citation, as well as @fulton2015, to place are results more clearly into a broader literature of MPA simulation (Line XX)

@@

*91: “equilibrium”. But most field studies won’t be measuring equilibrium, so herein lies an important difference?*

We have clarified that the simulation keeps track of outcomes at a variety of timesteps, including non-equilibrium. The "begins at" is just to clarify that we run the population out to equilibrium to start the simulation since there isn't an analytical solution to the biomass distribution in an age-structured spatial model when habitats vary.

@@

*105: so just to be clear, its not one mean density for inside, one for outside, but one mean density for everywhere?*

That is correct, so if the MPAs cover 50% of the habitat, MPAs cause biomass density goes 20% inside, 10% outside, our model would estimate 15%. We do however include site-specific intercepts that control for different mean baseline densities at each site, as well as site-specific environmental covariates (e.g. kelp cover) that can also account for some site specific differences.

@@

*Eqn 1: Don’t the gamma shape and scale depend on its mean? So maybe more correct to write this as: Expectation(d) = exp(beta….) and then say observations were sampled from a gamma, where the dispersion parameter was free/estimated.*

Thank you for the suggestion, in keeping with the likelihood notation here, we have kept the shape (dispersion) parameter in the equation, since the Gamma likelihood does depend on it, but you are right that the scale is a transformation of the mean and the shape and so should be (and has been) omitted.

@@

*It could be helpful to show an equation for the net DiD outcome (as explained at A.3). I think its something like: (D[post, fished]-D[pre, fished]) – (D[post, unfished]-D[pre, unfished])*

We agree this would help readers understand the model and have included this suggestion on line XX of the methods.

@@

*271: It would be good to read more comparison with the Nickols study, given the similarities to this study. In particular, they used a dynamic model to explore whether MPAs are achieving biomass recovery, also for Channel Islands. So how do their findings relate to what was found here?*

We briefly (due to word limit constraints) expanded our discussion of the synergies between our work and the Nickols study. Broadlyt we feel that the Nickols study further makes the case for...

One key difference is in the estimation strategy employed by our two studies. The Nickols approach might be considered a structural econometrics approach, in which we simulate the expected outcome in the absence of treatment, and then compare observed outcomes to the simulated. While they do not explicitly do so in their paper, their discussion of comparing the observed values to the expected baseline is in this vein. We on the other hand take an empirical approach, in which we construct the counterfactual "what would have happened without" the MPAs based on the observed trajectories of the non-targeted species (though in the same vein as Nickols et al. we simulate a counterfactual as well). Both of these approaches have strengths and weaknesses, and our studies share a common emphasis on the need for robust simulation modeling to ground expectations.

XX paragraph starting with "Stock assessment models that account for the population within the MPAs [@" XX

### 2020-11-25 documents/ovando-et-al-pop-effects-of-mpas-si.Rmd
updated draft

---
title: "Online Supporting Information"
subtitle: "Assessing the Population-level Conservation Effects of Marine Protected Areas"
output: 
  bookdown::word_document2:
    reference_docx: template.docx
  bookdown::pdf_document2:
    keep_tex: true
  pdf_document: default
bibliography: references.bib
header-includes:
    - \usepackage{longtable}
    - \usepackage{booktabs}
    - \usepackage{eso-pic}
    - \usepackage{graphicx}
    - \usepackage[left]{lineno}
    - \usepackage{xcolor}
params:
  run_name: ["v6.0"]
  sim_years: [50]
  burn_years: [20]
  num_patches: [25]
always_allow_html: true
---

@@

For the first synthetic control, we pulled our standardized mean index of abundance for targeted species as a whole from our difference-in-difference model as our treated group. We then pull the standardized indices of abundance for each of the non-targeted groups from the difference-in-difference to use as the candidate untreated components for the synthetic controls. A complete synthetic control analysis would require more extensive validation of the methods, but we use this approach simply to explore whether we observe substantially divergent results in the synthetic control versus the difference-in-difference model.

@@

```{r, include = FALSE, eval = FALSE}

@@

nontargeted_index <- data_frame(abundance_hat = fit_report$abundance_hat,
                               classcode = rep(1:n_distinct(used_data$classcode), each = length(years))) %>%
  mutate(log_abundance_hat = log(abundance_hat)) %>%
  group_by(classcode) %>%
  mutate(year =years) %>%
  mutate(scaled_abundance_hat = (abundance_hat - mean(abundance_hat)) / sd(abundance_hat)) %>%
  ungroup() %>%
  rename(numeric_classcode = classcode) %>%
  left_join(life_history, by = "numeric_classcode" ) %>% 
  left_join(unique(abundance_data$data[[1]] %>% select(classcode, targeted)), by = "classcode") %>% 
  filter(targeted == 0) %>% 
  select(log_abundance_hat, year, classcode, targeted)

targeted_index <- tmb_runs$tmb_fit[[1]]$zissou_estimates %>%
  filter(
    stringr::str_detect(variable, "(targeted_did_betas)"),!str_detect(variable, "non")
  ) %>%
  mutate(
    year = years,
    classcode = "targeted",
    targeted = 1
  ) %>%
  rename(log_abundance_hat = estimate) %>% 
  select(colnames(nontargeted_index))

  # filter(variable == "seeing_year_species_betas") %>%

@@

synth_data <- targeted_index %>% 
  bind_rows(nontargeted_index) %>% 
  left_join(synth_covariates, by = c("classcode","year")) %>% 
    mutate(numeric_classcode = as.numeric(factor(classcode))) %>% 
  group_by(classcode) %>% 
  mutate(log_abundance_hat = scale(exp(log_abundance_hat))) %>% 
  ungroup() %>% 
  as.data.frame() %>% 
  select(-rolling_mean)

@@

prepped_synth_data <-
  Synth::dataprep(
    foo = synth_data,
    predictors = colnames(synth_data)[str_detect(colnames(synth_data),"mean")],
    predictors.op = "mean",
    dependent = "log_abundance_hat",
    unit.variable = "numeric_classcode",
    unit.names.variable = "classcode",
    time.variable = "year",
    treatment.identifier = "targeted",
    controls.identifier = unique(synth_data$classcode)[unique(synth_data$classcode) != "targeted"],
    time.predictors.prior = years[years <= 2003],
    time.optimize.ssr = years[years <= 2003],
    time.plot = years
  )

@@

```{r  total-synth, fig.cap = "Difference in centered and scaled standardized targeted abundance and synthetic standardized targeted abundance", eval=FALSE}
total_gap_plot
```

```{r raw-synth, include = FALSE, eval = FALSE}

  consistent_classcodes <- used_data %>%
      group_by(classcode, region) %>%
      filter(any_seen) %>%
      summarise(n_years = n_distinct(year)) %>%
      ungroup() %>%
      filter(n_years == n_distinct(used_data$year))

synth_data <- used_data %>% 
  filter(classcode %in% consistent_classcodes$classcode,
         region %in% consistent_classcodes$region) %>% 
  mutate(classcode = ifelse(targeted == 1, "targeted", classcode),
         region = ifelse(targeted == 1, "targeted", region)) %>% 
      group_by(year,
               site_side,
               region,
               zone,
               transect,
               eventual_mpa,
               classcode,
               targeted) %>%
      summarise(
        total_classcode_density = sum(exp(log_density)),
        var_tex = sum(cumulative_n_obs),
        var_vis = mean(mean_vis),
        var_temp = mean(mean_temp),
        var_depth = mean(mean_depth),
        var_surge = mean(surge),
        var_kelp = mean(interp_kelp)
      ) %>%  # sum density across all levels of a transect
      group_by(year, site_side, region, eventual_mpa, classcode, targeted) %>%
      summarise(
        md = mean(total_classcode_density),
        var_tex = mean(var_tex),
        var_vis = mean(var_vis),
        var_temp = mean(var_temp),
        var_depth = mean(var_depth),
        var_surge = mean(var_surge),
        var_kelp = mean(var_kelp)
      ) %>% # calculate mean density per year site, side, species, averaging over zone, transect
      ungroup()

 synth_data <- synth_data %>% 
     group_by(year,region,classcode,targeted) %>%
      summarise(
        total_biomass_density = (sum(md) / 1e6) * 10000,
        # calculate total and mean biomass densities across all species per year site side
        mean_biomass_density = log((mean(md) / 1e6) * 10000 + 1e-3),
        var_tex = mean(var_tex),
        var_vis = mean(var_vis),
        var_temp = mean(var_temp),
        var_kelp = mean(var_kelp)
      ) %>%
   ungroup() %>% 
   mutate(classcode = ifelse(targeted == 1, classcode, paste(classcode, region, sep = '_'))) %>% 
      mutate(numeric_classcode = as.numeric(factor(classcode))) %>% 
   as.data.frame()

prepped_synth_data <-
  Synth::dataprep(
    foo = synth_data,
    predictors = colnames(synth_data)[str_detect(colnames(synth_data),"var")],
    predictors.op = "mean",
    dependent = "mean_biomass_density",
    unit.variable = "numeric_classcode",
    unit.names.variable = "classcode",
    time.variable = "year",
    treatment.identifier = "targeted",
    controls.identifier = unique(synth_data$classcode[synth_data$targeted == 0]),
    time.predictors.prior = years[years <= 2003],
    time.optimize.ssr = years[years <= 2003],
    time.plot = years
  )

total_gap_plot <- gaps %>% 
  ggplot(aes(year, gap)) + 
  # geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_vline(aes(xintercept = 2003), color = "red")+
  geom_line() + 
    labs(x = "Year", y = "Standard deviations from synthetic control")

@@

```{r, include = FALSE, eval=FALSE}

@@

    prepped_synth_data <-
      Synth::dataprep(
        foo = temp_synth_data,
        predictors = colnames(temp_synth_data)[str_detect(colnames(temp_synth_data), "mean")],
        predictors.op = "mean",
        dependent = "log_abundance_hat",
        unit.variable = "numeric_classcode",
        unit.names.variable = "classcode",
        time.variable = "year",
        treatment.identifier = treated_classcode,
        controls.identifier = unique(temp_synth_data$classcode)[unique(temp_synth_data$classcode) != treated_classcode],
        time.predictors.prior = c(2000:2003),
        time.optimize.ssr = c(2000:2003),
        time.plot = years
      )

@@

nontargeted_index <- data_frame(abundance_hat = fit_report$abundance_hat,
                               classcode = rep(1:n_distinct(used_data$classcode), each = length(years))) %>%
  mutate(log_abundance_hat = log(abundance_hat)) %>%
  group_by(classcode) %>%
  mutate(year = 1999 + 1:length(abundance_hat)) %>%
  mutate(scaled_abundance_hat = (abundance_hat - mean(abundance_hat)) / sd(abundance_hat)) %>%
  ungroup() %>%
  rename(numeric_classcode = classcode) %>%
  left_join(life_history, by = "numeric_classcode" ) %>% 
  left_join(unique(abundance_data$data[[1]] %>% select(classcode, targeted)), by = "classcode") %>% 
  select(log_abundance_hat, year, classcode, targeted)

@@

synth_data <- nontargeted_index %>% 
  left_join(synth_covariates, by = c("classcode","year")) %>% 
    mutate(numeric_classcode = as.numeric(factor(classcode))) %>% 
  group_by(classcode) %>% 
  mutate(log_abundance_hat = scale(exp(log_abundance_hat))) %>% 
  ungroup() %>% 
  as.data.frame()

@@

```{r synth-classcode-fits, fig.cap="Synthetic control gaps for each targeted species", eval=FALSE}
synth_classcode_fits_plot + 
  theme_minimal()
```

>>>>

---
title: "Online Supporting Information"
subtitle: "Assessing the Population-level Conservation Effects of Marine Protected Areas"
output: 
  bookdown::pdf_document2:
    keep_tex: true
  bookdown::word_document2:
    reference_docx: template.docx
  pdf_document: default
bibliography: references.bib
header-includes:
    - \usepackage{longtable}
    - \usepackage{booktabs}
    - \usepackage{eso-pic}
    - \usepackage{graphicx}
    - \usepackage[left]{lineno}
    - \usepackage{xcolor}
params:
  run_name: ["v6.0"]
  sim_years: [50]
  burn_years: [20]
  num_patches: [25]
always_allow_html: true
---

@@

For the first synthetic control, we first calculated the mean total biomass density of targeted species across the Channel Islands, our outcome variable of interest. We then calculated the mean total biomass dentisy of each individual non-targeted species in our database as a set of donor data to construct our synthetic control. A complete synthetic control analysis would require more extensive validation of the methods, but we use this approach simply to explore whether we observe substantially divergent results in the synthetic control versus the difference-in-difference model.

@@

```{r, include = FALSE, eval = TRUE}

@@

targeted_index <- base_run$did_fit[[1]]$did_data %>%
  group_by(year, targeted) %>%
  summarise(mtbd = mean(total_biomass_density)) %>%
  group_by(targeted) %>%
  filter(targeted == 1) %>% 
  mutate(classcode = "targeted")

nontargeted_index <- abundance_data$data[[which(abundance_data$data_source == "pisco")]] %>% 
  group_by(year, targeted, classcode, site_side) %>% 
  summarise(tb = sum(total_biomass_g)) %>% 
  group_by(year, targeted, classcode) %>% 
  summarise(mtbd = mean(tb)) %>% 
  filter(targeted == 0) %>% 
  ungroup() %>% 
  select(colnames(targeted_index))

@@

synth_data <- targeted_index %>% 
  bind_rows(nontargeted_index) %>% 
  left_join(synth_covariates, by = c("classcode","year")) %>% 
  ungroup() %>% 
  mutate(numeric_classcode = as.numeric(factor(classcode))) %>% 
  group_by(classcode) %>% 
  mutate(scaled_mtbd = as.numeric(scale(mtbd))) %>% 
  ungroup() %>% 
  as.data.frame()  %>% 
  select(-rolling_mean)

@@

synth_data %>% 
  group_by(numeric_classcode, year) %>% 
  count()

prepped_synth_data <-
  Synth::dataprep(
    foo = synth_data,
    predictors = colnames(synth_data)[str_detect(colnames(synth_data),"mean")],
    predictors.op = "mean",
    dependent = "scaled_mtbd",
    unit.variable = "numeric_classcode",
    unit.names.variable = "classcode",
    time.variable = "year",
    treatment.identifier = "targeted",
    controls.identifier = unique(synth_data$classcode)[unique(synth_data$classcode) != "targeted"],
    time.predictors.prior = years[years <= 2003],
    time.optimize.ssr = years[years <= 2003],
    time.plot = years
  )

@@

```{r  total-synth, fig.cap = "Difference in centered and scaled standardized targeted abundance and synthetic standardized targeted abundance", eval=TRUE}
total_gap_plot
```

@@

```{r, include = FALSE, eval=TRUE}

@@

    prepped_synth_data <-
      Synth::dataprep(
        foo = temp_synth_data,
        predictors = colnames(temp_synth_data)[str_detect(colnames(temp_synth_data), "mean")],
        predictors.op = "mean",
        dependent = "scaled_mtbd",
        unit.variable = "numeric_classcode",
        unit.names.variable = "classcode",
        time.variable = "year",
        treatment.identifier = treated_classcode,
        controls.identifier = unique(temp_synth_data$classcode)[unique(temp_synth_data$classcode) != treated_classcode],
        time.predictors.prior = c(2000:2003),
        time.optimize.ssr = c(2000:2003),
        time.plot = years
      )

@@

nontargeted_index <- abundance_data$data[[which(abundance_data$data_source == "pisco")]] %>% 
  group_by(year, targeted, classcode, site_side) %>% 
  summarise(tb = sum(total_biomass_g)) %>% 
  group_by(year, targeted, classcode) %>% 
  summarise(mtbd = mean(tb)) %>% 
  ungroup() %>% 
  select(colnames(targeted_index))

@@

synth_data <- nontargeted_index %>% 
  left_join(synth_covariates, by = c("classcode","year")) %>% 
    mutate(numeric_classcode = as.numeric(factor(classcode))) %>% 
  group_by(classcode) %>% 
  mutate(scaled_mtbd = scale(mtbd)) %>% 
  ungroup() %>% 
  as.data.frame()

@@

```{r synth-classcode-fits, fig.cap="Synthetic control gaps for each targeted species", eval=TRUE}
synth_classcode_fits_plot + 
  theme_minimal()
```
